Studying the Performance of the Jellyfish Search Optimiser for the Application of Projection Pursuit

### 2024-07-17 jso.tex
fixed a typo in bibliography

\begin{tcolorbox}[enhanced jigsaw, breakable, opacitybacktitle=0.6, colframe=quarto-callout-note-color-frame, opacityback=0, arc=.35mm, toptitle=1mm, leftrule=.75mm, colbacktitle=quarto-callout-note-color!10!white, bottomtitle=1mm, left=2mm, titlerule=0mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, toprule=.15mm, coltitle=black, rightrule=.15mm, bottomrule=.15mm, colback=white]

>>>>

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, bottomrule=.15mm, title={Algorithm: Jellyfish Optimizer Pseudo Code}, breakable, toptitle=1mm, colframe=quarto-callout-note-color-frame, titlerule=0mm, opacityback=0, opacitybacktitle=0.6, coltitle=black, leftrule=.75mm, colback=white, arc=.35mm, bottomtitle=1mm, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm]
